Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-24 manuscript/climate_sensitivity_draft.Rmd
word count, minor shortening in results
#117

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  5,365	 |	No. of figures | 	4 (all colour)
Summary|  	198 | 	No. of Tables | 	3  
Introduction|	1,034 |	No of Supporting Information files | 	14
Materials and Methods |	1,945	||	 
Results |	697	 ||
Discussion |	1467	||
Acknowledgements | 125	||

@@

In contrast, $PLA_{dry}$, and $\pi_{tlp}$ were both negatively correlated to drought resistance (Figs. **4, S6**; Tables 1,S4-S7). 
Both had consistent signs across all droughts, and their inclusion at least marginally improved the model ($\Delta$AICc > 1.0) for at least one of the three droughts (Table S4), qualifying them as candidate variables for the full model. 
$PLA_{dry}$ had a significant influence, with negative coefficient, in full models for the three droughts combined and for the 1966 drought individually (Fig. **4**; Tables S6-S7). 
For 1977 and 1999, it was included with a negative coefficient in some of the top models (Tables S6-S7).
$\pi_{tlp}$ was included with a negative coefficient in the best model for both all droughts combined and for the 1977 drought individually (Fig. **4**; Table S6). 
It was also included in some of the top models for 1999 (Tables S6-S7).

>>>>

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) | 6,490	 |	No. of figures | 	4 (all colour)
Summary|  	198 | 	No. of Tables | 	3  
Introduction|	1,264 |	No of Supporting Information files | 	14
Materials and Methods |	2,228	||	 
Results |	929	 ||
Discussion |	1927	||
Acknowledgements | 142	||

@@

In contrast, $PLA_{dry}$, and $\pi_{tlp}$ - the traits that qualified for inclusion in the full model (Table S4) - were both negatively correlated to drought resistance (Figs. **4, S6**; Tables 1,S4-S7). 
$PLA_{dry}$ had a significant influence, with negative coefficient, in full models for the three droughts combined and for the 1966 drought individually (Fig. **4**; Tables S6-S7). 
For 1977 and 1999, it was included with a negative coefficient in some of the top models (Tables S6-S7).
$\pi_{tlp}$ was included with a negative coefficient in the best model for both all droughts combined and for the 1977 drought individually (Fig. **4**; Table S6). 
It was also included in some of the top models for 1999 (Tables S6-S7).
